Interval Probability for Fuzzy Quantum Theories

### 2016-05-29 prob.tex
prob.tex \subsection{Measuring Probabilities: Buffon's Needle Problem} Updating the law of large numbers...

In previous section, we assume the probability of each event is known
a priori.

@@

>>>>

In previous section, we assume the probability of each event is known
a priori. In reality, we seldom know much about events, but we assume
each event~$E$ has a probability~$\pmeas(E)$. $\pmeas(E)$ could
be approximated by the relative frequency~$\frac{1}{N}\sum_{i}x_{i}$,
where $x_{i}$ is the outcome of $i$-th trial within total $N$ independent
trials. This fact is called by the law of large numbers~\cite{Bernoulli1713,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.

@@

Recall that the relative frequency will approximate the probability
of an event if the event has a probability. What if the event doesn't
have infinity precise probability because of the experimental limit?
In this case, two sequences of independent copies of experimental
results can have their relative frequencies converge almost surely
to different limits~\cite{Marinacci1999,Teran2014}. In another word,
to get a better approximation of the probability, the quality of experimental
equipment cannot be compensated by the number of independent trials.
